---
title: "Final Project"
output:
  html_document:
    df_print: paged
---

OVERALL QUESTION I AM TRYING TO ANSWER: Does age have an impact on WHERE people shop (ie. online, in store, through a catalog)

Necessary Imports
```{r}
library(ggplot2)
library(e1071)
library(dplyr)
```

First I am reading in the CSV file.
```{r}
data <- read.csv("~/Desktop/INFO_659/final_project/marketing_campaign.csv")
head(data)
```

Now I am checking the data for null values.
```{r}
is.null(data)
```
Now that we know the data doesn't contain any nulls, we can move forward.


First I will be creating an 'age' variable which takes the year a customer was born and subtracts that from 2021 to get the customers age.
```{r}
data$age <- 2021 - data['Year_Birth']
data$age <- as.numeric(unlist(data$age))
```

Now I will create a histogram of the age data to get a better understanding of the customers on this data set.
```{r}
hist(data$age)
``` 
As you can see, this histogram seems pretty normally distributed.  To accurately use this data I will be turning the age variable into a categorical one by seperating each age into four different categories: 20-35, 36-50, 51-65, and 66+.

```{r}
data <- within(data, {   
  ageCat <- NA # need to initialize variable
  ageCat[age < 35] <- "20-35"
  ageCat[age >= 35 & age < 50] <- "35-49"
  ageCat[age >= 50 & age < 65] <- "50-64"
  ageCat[age >= 65] <- "65+"
   } )

head(data$ageCat)
```

Next, I am looking at the frequency of where each age group tends to make their purchases.
```{r}
xtabs(~ageCat+NumWebPurchases, data = data)
xtabs(~ageCat+NumCatalogPurchases, data = data)
xtabs(~ageCat+NumStorePurchases, data = data)
```

Now I am graphing each of these variables against age to visually see what is going on.

```{r}
data %>%
  ggplot(aes(x=ageCat, y=NumWebPurchases, fill = ageCat)) +
  geom_boxplot() +theme_bw()+
  ggtitle("Box Plot")
```
```{r}
data %>%
         ggplot(aes(x=ageCat, y=NumCatalogPurchases, fill = ageCat)) +
         geom_boxplot() +theme_bw()+
         ggtitle("Box Plot")
```

```{r}
data %>%
         ggplot(aes(x=ageCat, y=NumStorePurchases, fill = ageCat)) +
         geom_boxplot() +theme_bw()+
         ggtitle("Box Plot")
```
It seems as though each age group is pretty similar in their spending ways.


Now, I will be conducting naive bayes on NumWebPurchases, NumCatalogPurchases and NumStorePurchases.
```{r}
#model <- naiveBayes(ageCat ~ NumWebPurchases + NumCatalogPurchases + NumStorePurchases, data = train, usekernel = T, laplace = 1.5) 
#model
```
As you can see, none of these are statistically significant.  Thus, you cannot assume where someone may make a purchase simply by using their age. 


